\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-01-02 AffineLieAlgebras/InformalNotes/article.tex
Pdf update

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}

@@

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}

%\usepackage{verbatim} 
\newenvironment{comment}
{\par\noindent{\bf TODO}\\}
{\\\hfill$\scriptstyle\blacksquare$\par}

\theoremstyle{definition} \newtheorem{Def}{Definition}

@@

\begin{comment}
  We need to proof the following:
  For the Weyl group $W_{\mathfrak{a}}$ any element $\omega in W$ such that $\omega\cdot W_{\mathfrak{a}} \cdot \omega = W_{\mathfrak{a}}$ has the form $\omega=r_1^{s_1} r_2^{s_2}\dots r_k^{s_k}$ where $r_1\dots r_k$ are the generators corresponding to the nodes of non-connected component if $\mathfrak{g}=A_n, C_n, D_n$. 
  For $\mathfrak{g}=B_n$ there exist additional elements $\{\omega=r_1^{s_1} r_2^{s_2}\dots r_k^{s_k}\cdot r_{k+1}^{s_{k+1}} r_{k+2}^{s_{k+2}}\}$. 
\end{comment}
